---
title: "NFL Dynasty Report - Week 14"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Dan Coulton"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown
---

```{r setup, include = F, message = F}
library(tidyverse)
library(jsonlite)
library(httr)
library(ffscrapr)
library(linprog)
library(kableExtra)
library(rmarkdown)
library(plotly)
library(formattable)
library(rmdformats)

setwd('C:/Users/danie/OneDrive/Documents/DynastyNFL/')
taxi_squad <- readRDS('Taxi_2021.RDS') %>% 
  mutate(week_activated = case_when(full_name=='Michael Carter' ~ 3,
                                    full_name=='Chuba Hubbard' ~ 4,
                                    full_name=='Khalil Herbert' ~ 6,
                                    full_name=='Mac Jones' ~ 9,
                                    full_name=="D'Wayne Eskridge" ~ 10,
                                    full_name=='Elijah Mitchell' ~ 10,
                                    full_name=='Elijah Moore' ~ 12,
                                    full_name=='Tee Higgins' ~ 13,
                                    T ~ 0))
season <- 2021

#league_id <- sleeper_userleagues('DanCoulton') %>% filter(league_name == 'NFL Dynasty') %>% pull(league_id)
league_id <- 659068468825530368
dynasty_conn <- sleeper_connect(season = season, league_id = league_id)

ff_league <- ff_league(dynasty_conn)

gameweek_start <- 1
gameweek_end <- 14
league_size <- as.numeric(ff_league$franchise_count)
sims <- 100
draft_rounds <- 4
# add Matt Breida to Joe's week 10 (16.5 points)

### In the pipeline ###
# Next week preview
# Add draft pick range

```

```{r get players, include = F, message = F}
# title: "NFL Dynasty Report - Week `r gameweek_end` Recap"

if(!exists('get_players')) {get_players <- GET('https://api.sleeper.app/v1/players/nfl')}
json_players_parsed <- content(get_players,as='parsed')

datalist = list()
for (i in 1:length(json_players_parsed)) {
  df<-data.frame(t(unlist(json_players_parsed[[i]],recursive = TRUE,use.names = TRUE)))
  datalist[[i]] <- df
}
player_data <-bind_rows(datalist)

remove(df,datalist,i, json_players_parsed)

```

```{r user info, include = F, message = F}

rostersRaw <- GET(paste("https://api.sleeper.app/v1/league/",league_id,"/rosters",sep=""))
rostersParsed <- content(rostersRaw,as="parsed")

########### User Info ###########
usersRaw <- fromJSON(paste("https://api.sleeper.app/v1/league/",league_id,"/users",sep=""), flatten = TRUE)

datalist = list()
for (i in 1:league_size) {
  df<-data.frame(t(unlist(rostersParsed[i]))) %>%
    select(owner_id, roster_id)
  
  datalist[[i]] <- df
}
user_info <- data.frame(bind_rows(datalist)) %>% 
  left_join(usersRaw[, c('user_id', 'display_name', 'metadata.team_name')], by = c('owner_id' = 'user_id')) %>% 
  rename(Manager = display_name)

```

```{r taxi creation, include = F, message = F}
### This only needs to be run if it doesn't previously exist in the setup chunk, or if players are activated from the taxi squad  ###

datalist = list()
for (i in 1:league_size) {
  df<-data.frame(t(unlist(rostersParsed[i]))) %>%
    select(roster_id, starts_with('taxi')) %>%
    pivot_longer(cols = starts_with('taxi'), names_to = 'taxi_id', values_to = 'player_id') %>%
    left_join(player_data[, c('full_name', 'position', 'player_id', 'team')], by = 'player_id') %>%
    mutate(taxi_id = substr(taxi_id, 5, 5), week_activated = 0)

  datalist[[i]] <- df
}
# taxi_squad <-data.frame(bind_rows(datalist))
remove(df,datalist,i,rostersParsed,rostersRaw, usersRaw)

#saveRDS(taxi_squad, 'Taxi_2021.RDS')

```

```{r get matchups, include = F, message = F}

datalist_gameweek = list()
for (i in gameweek_start:14) {
  matchupRaw <- GET(paste('https://api.sleeper.app/v1/league/',league_id,'/matchups/', i, sep=""))
  matchupParsed <- content(matchupRaw, as="parsed")
  
  datalist_matchup = list()
  for (j in 1:league_size) {
    df <- data.frame(t(unlist(matchupParsed[j]))) %>% 
      select(roster_id, matchup_id, starts_with('players_points')) %>% 
      pivot_longer(cols = starts_with('players_points'), names_to = 'player_id', values_to = 'points') %>% 
      mutate(player_id = substr(player_id, 16, length(player_id)),
             matchup_id = as.numeric(matchup_id),
             points = as.numeric(points))
    
    starters <- data.frame(t(unlist(matchupParsed[j]))) %>% 
      select(roster_id, matchup_id, starts_with('starters'), -starts_with('starters_')) %>% 
      pivot_longer(cols = starts_with('starters'), names_to = 'starter_id', values_to = 'player_id') %>% 
      mutate(starter_ind = 1)
    
    df <- df %>% 
      left_join(starters[c('player_id', 'starter_ind')], by = 'player_id')
      
    datalist_matchup[[j]] <- df
  }
  datalist_gameweek[[i]] <-bind_rows(datalist_matchup) %>% 
    mutate(gameweek = i)
}
matchup_data <-bind_rows(datalist_gameweek) %>% 
  left_join(player_data[, c('full_name', 'position', 'player_id', 'team')], by = 'player_id') %>% 
  mutate(full_name = if_else(position=='DEF', player_id, full_name),
         starter_ind = if_else(is.na(starter_ind), 0, 1)) %>% 
  left_join(taxi_squad[, c('player_id', 'week_activated')], by = 'player_id') %>% 
  filter(is.na(week_activated) | (week_activated<=gameweek & week_activated>0)) %>% 
  left_join(user_info[, c('roster_id', 'Manager')], by = 'roster_id') %>% 
  rename(Points = points)

remove(df,datalist_matchup, datalist_gameweek, i, j, matchupRaw, matchupParsed)

matchup_id <- matchup_data %>% 
  distinct(roster_id, matchup_id, gameweek) %>% 
  left_join(x=., y=., by = c('matchup_id', 'gameweek')) %>% 
  rename(roster_id = roster_id.x, opponent_id = roster_id.y) %>% 
  filter(roster_id!=opponent_id)

```

```{r get historic scores, include = F, message = F}

league_id2020 <- '524711968751366144'
league_id2019 <- '401733459510312960'

### 2019 ###
datalist_gameweek = list()
for (i in gameweek_start:16) {
  matchupRaw <- GET(paste('https://api.sleeper.app/v1/league/',league_id2019,'/matchups/', i, sep=""))
  matchupParsed <- content(matchupRaw, as="parsed")
  
  datalist_matchup = list()
  for (j in 1:league_size) {
    df <- data.frame(t(unlist(matchupParsed[j]))) %>% 
      select(roster_id, points)
    
    datalist_matchup[[j]] <- df
  }
  datalist_gameweek[[i]] <-bind_rows(datalist_matchup) %>% 
    mutate(gameweek = i)
}
matchup_data2019 <-bind_rows(datalist_gameweek) %>% 
  mutate(season = 2019)

### 2020 ###
datalist_gameweek = list()
for (i in gameweek_start:16) {
  matchupRaw <- GET(paste('https://api.sleeper.app/v1/league/',league_id2020,'/matchups/', i, sep=""))
  matchupParsed <- content(matchupRaw, as="parsed")
  
  datalist_matchup = list()
  for (j in 1:league_size) {
    df <- data.frame(t(unlist(matchupParsed[j]))) %>% 
      select(roster_id, points)
    
    datalist_matchup[[j]] <- df
  }
  datalist_gameweek[[i]] <-bind_rows(datalist_matchup) %>% 
    mutate(gameweek = i)
}
matchup_data2020 <-bind_rows(datalist_gameweek) %>% 
  mutate(season = 2020)

### 2021 ###
datalist_gameweek = list()
for (i in gameweek_start:gameweek_end) {
  matchupRaw <- GET(paste('https://api.sleeper.app/v1/league/',league_id,'/matchups/', i, sep=""))
  matchupParsed <- content(matchupRaw, as="parsed")
  
  datalist_matchup = list()
  for (j in 1:league_size) {
    df <- data.frame(t(unlist(matchupParsed[j]))) %>% 
      select(roster_id, points)
    
    datalist_matchup[[j]] <- df
  }
  datalist_gameweek[[i]] <-bind_rows(datalist_matchup) %>% 
    mutate(gameweek = i)
}
matchup_data2021 <-bind_rows(datalist_gameweek) %>% 
  mutate(season = 2021) %>% 
  filter(gameweek<gameweek_end)

score_data_historic <- bind_rows(matchup_data2019, matchup_data2020, matchup_data2021)
rm(matchup_data2019, matchup_data2020, matchup_data2021, datalist_gameweek, datalist_matchup)

```

# Playoff Hunt

The hunt for the playoffs as it stands. All-play is the record if all teams were to play each other every week. xWins is the number of wins you would have expected so far based on the all-play record. The playoff and bye % is calculated by randomly assigning each team a weekly score (from any team) since the league began in 2019. `r as.character(sims)` different seasons have been simulated using the wins to date and the remaining fixtures for each team. Strength of roster isn't taken into account in these calculations.

``` {r playoff hunt, echo = F, message = F}

pts_week <- matchup_data %>% 
  filter(starter_ind==1) %>% 
  group_by(gameweek, roster_id, Manager) %>% 
  summarise(pts = sum(Points)) %>% 
  left_join(matchup_id[, c('opponent_id', 'roster_id', 'gameweek')], by = c('gameweek', 'roster_id')) %>% 
  left_join(x=., y=.[, c('gameweek', 'opponent_id', 'pts')], by = c('gameweek', 'roster_id' = 'opponent_id')) %>% 
  rename(pts = pts.x, pts_opponent = pts.y) %>% 
  mutate(win = if_else(pts > pts_opponent, 1,
                       if_else(pts_opponent > pts, 0, 0.5))) %>% 
  ungroup %>% 
  group_by(gameweek) %>% 
  mutate(all_play = rank(pts)-1) %>% 
  left_join(matchup_id[, c('matchup_id', 'roster_id', 'gameweek')], by = c('roster_id', 'gameweek'))

datalist_sim = list()
for (i in 1:sims) {
  set.seed(i)
  gameweek_sim <- matchup_data %>%
    select(matchup_id, gameweek) %>% 
    distinct() %>% 
    rowwise() %>% 
    mutate(home_pts = sample(as.numeric(score_data_historic$points), 1, replace=F),
           away_pts = sample(as.numeric(score_data_historic$points), 1, replace=F),
           away_pts = if_else(home_pts==away_pts, away_pts+sample(c(-1,1), 1), away_pts))
  
  pts_sim <- pts_week %>% 
    left_join(gameweek_sim, by = c('matchup_id', 'gameweek')) %>% 
    mutate(roster_id = as.numeric(roster_id),
           opponent_id = as.numeric(opponent_id),
           win_sim = if_else(roster_id<opponent_id, if_else(home_pts>away_pts, 1, 0), if_else(away_pts>home_pts, 1, 0)),
           win_sim = if_else(gameweek>gameweek_end, win_sim, win),
           pts_sim = if_else(roster_id<opponent_id, home_pts, away_pts),
           pts_sim = if_else(gameweek>gameweek_end, pts_sim, pts),
           nxt_wk_win = if_else(gameweek==gameweek_end+1, win_sim, 0))
  
  table_sim <- pts_sim %>% 
    group_by(Manager) %>% 
    summarise(Wins = sum(win_sim),
              Points = sum(pts_sim),
              Upcoming = sum(nxt_wk_win)) %>% 
    arrange(desc(Wins), desc(Points)) %>% 
    mutate(Position = seq.int(nrow(.)),
           Playoff = if_else(Position<=6, 1, 0),
           Bye = if_else(Position<=2, 1, 0)) %>% 
    ungroup
  
  datalist_sim[[i]] = table_sim
}
sim_wins_raw <- bind_rows(datalist_sim)

sim_wins <- sim_wins_raw %>% 
  group_by(Manager) %>% 
  summarise(`Playoff %` = round(mean(Playoff)*100, 1),
            `Bye %` = round(mean(Bye)*100, 1))
rm(table_sim, i, pts_sim, gameweek_sim, datalist_sim)

pts_season <- pts_week %>%
  filter(gameweek<=gameweek_end) %>% 
  group_by(Manager) %>% 
  summarise(Wins = sum(win),
            Points = sum(pts),
            All_Play = sum(all_play)) %>% 
  arrange(desc(Wins), desc(Points)) %>% 
  mutate(`All-Play` = paste0(All_Play,'-', (league_size-1)*(gameweek_end-gameweek_start+1)-All_Play),
         xWins = round(All_Play/(league_size-1), 1),
         WOE = Wins - xWins,
         Position = league_size + 1 - rank(Wins + Points/10000)) %>% 
  left_join(sim_wins, by = 'Manager')

pts_season %>% 
  select(Position, Manager, Wins, Points, `All-Play`, xWins, `Playoff %`, `Bye %`) %>%
  knitr::kable(format = 'html', align = c('c', 'l', rep('c', 6)), escape = F) %>% 
  kable_styling(bootstrap_options = c('striped', 'responsive', 'hover'),
                full_width = F,
                position = 'left') %>% 
  row_spec(1:2, bold = T, color = 'white', background = '#0080ff') %>% 
  row_spec(3:6, bold = T, color = 'white', background = '#79c973') %>% 
  row_spec(7:12, bold = T, color = 'white', background = '#ff6666')

```

Wins over expectation (WOE) looks at the relationship between actual wins and all-play wins. This shows how lucky or unlucky a team has been with the schedule.

Teams above the black line have been more fortunate with their schedule and teams below have been unlucky with the opponents they have faced.

``` {r wins vs expectation, echo = F, message = F}

pts_season %>% 
  ungroup() %>% 
  plot_ly() %>% 
  add_trace(x = ~xWins, y = ~Wins, mode = 'markers', color = ~Manager, colors = 'Paired',
            hovertemplate = paste(pts_season$Manager, '<br> Expected Wins: %{x}', '<br> Actual Wins: %{y}', '<extra></extra>')) %>% 
  add_trace(x = seq(0, gameweek_end), y = seq(0, gameweek_end), mode = 'lines', line = list(color = 'black', width = 0.5), showlegend = F) %>% 
  layout(title = 'Wins vs Expected Wins',
         xaxis = list(title = 'Expected Wins', tick0=1, dtick=1, fixedrange = TRUE),
         yaxis = list(title = 'Actual Wins', tick0=1, dtick=1, fixedrange = TRUE),
         hovermode = 'compare',
         legend = list(title=list(text='<b> Manager </b>'))) %>% 
  plotly::style(hoverinfo = 'none')
  #add_text(textposition = 'top')

```

`r pts_season %>% filter(WOE == max(WOE)) %>% pull(Manager)` has been the luckiest so far, with `r pts_season %>% filter(WOE == max(WOE)) %>% pull(WOE) %>% nth(1)` more wins than expected.

`r pts_season %>% filter(WOE == min(WOE)) %>% pull(Manager)` can feel hard done by, with `r pts_season %>% filter(WOE == min(WOE)) %>% mutate(WOE = -WOE) %>% pull(WOE) %>% nth(1)` fewer wins than expected.

<br>

# Story of the Season

The following chart shows the performance of each team as the season has progressed. This is calculated as the xWins for each week minus the average wins each week (0.5). This strips out any influence of matchup and purely looks at your points position in a given week.

For example, an increasing line in the first half of the season followed by a decreasing line over the second half would signify good performance to start the year, but a poor run to end the season.

``` {r xwins vs average, echo = F, message = F}

xWins_vs_avg <- pts_week %>% 
  filter(gameweek<=gameweek_end) %>% 
  mutate(xWins = all_play/11) %>% 
  group_by(Manager) %>% 
  mutate(cum_Wins = cumsum(win),
         cum_xWins = round(cumsum(xWins), 1),
         win_diff = cum_xWins - gameweek/2)

xWins_vs_avg |> 
  ungroup() |> 
  plot_ly(y = ~win_diff) |> 
  add_trace(x = ~gameweek, color = ~Manager, type = 'scatter', mode = 'lines', colors = 'Paired', text = ~Manager,
            hovertemplate = paste('Week %{x}', '<br>%{text}', '<br>xWins vs Avg: %{y}', '<extra></extra>')) |> 
  layout(title = 'xWins vs Average over the Season',
         xaxis = list(title = 'Week',fixedrange = TRUE, tickmode = 'linear'),
         yaxis = list(title = 'xWins vs Average',  categoryorder = "array", categoryarray = ~win_diff, tick0=1, dtick=1, fixedrange = TRUE),
         legend = list(title=list(text='<b> Manager </b>')))

```
<br>

# League Position Tracker

The next table tracks the league position by week for each team in the league. To isolate a single team's record, double click on the legend on the right.

``` {r position chart, echo = F, message = F}

position <- pts_week %>% 
  filter(gameweek<=gameweek_end) %>% 
  group_by(Manager) %>% 
  summarise(csum_win = cumsum(win),
            csum_pts = cumsum(pts)) %>% 
  mutate(gameweek = rep(1:gameweek_end)) %>% 
  ungroup() %>% 
  group_by(gameweek) %>% 
  mutate(Position = league_size + 1 - rank(csum_win + csum_pts/10000))

position %>% 
  ungroup() %>% 
  plot_ly(y = ~Position) %>% 
  add_trace(x = ~gameweek, color = ~Manager, type = 'scatter', mode = 'lines+markers', colors = 'Paired', text = ~Manager, color = ~Manager,
            hovertemplate = paste('Week %{x}', '<br> %{text}', '<br> Position: %{y}', '<extra></extra>')) %>% 
  layout(title = 'League Position by Week',
         xaxis = list(title = 'Week',fixedrange = TRUE, tickmode = 'linear'),
         yaxis = list(title = 'League Position',  categoryorder = "array", categoryarray = ~Position, autorange = 'reversed', tick0=1, dtick=1,
                      range=c(1,12), fixedrange = TRUE),
         legend = list(title=list(text='<b> Manager </b>')))

```

<br>

```{r calculate potential points, include = F}

datalist_i = list()
datalist_j = list()
for (i in gameweek_start:gameweek_end) {
  for (j in 1:league_size) {
    match_result <- matchup_data %>% 
      filter(roster_id==j, gameweek==i)
    
    constraints_matrix=matrix(c(match_result$position=='QB',
                                match_result$position=='RB',
                                match_result$position=='WR',
                                match_result$position=='TE',
                                match_result$position=='RB',
                                match_result$position=='WR',
                                match_result$position=='TE',
                                match_result$position=='K',
                                match_result$position=='DEF'),
                              byrow=T,nrow=9)
    
    objective_vector <- c(match_result$Points)
    constraints_matrix <- rbind(constraints_matrix, diag(dim(match_result)[1]), rep(1,dim(match_result)[1]))
    constraints_vector <- c(1, 2, 2, 1, 4, 4, 4, 1, 1, rep(1,dim(match_result)[1]), 10)
    
    sol_pp <- lp(direction='max',objective.in = objective_vector, const.rhs = constraints_vector,
                 const.mat = constraints_matrix, const.dir = c('=', rep('>=',3), rep('<=',3), rep('=',2), rep('<=',dim(match_result)[1]), '='), all.bin = T)
    sol_pp$solution
    sol_pp$objval
    
    datalist_j[[j]] <- match_result %>% mutate(pp_starter = sol_pp$solution, potential_points = pp_starter * Points)
  }
  datalist_i[[i]] <-bind_rows(datalist_j)
}
pp_player <- bind_rows(datalist_i)
rm(datalist_i, datalist_j, sol_pp, match_result, constraints_matrix, objective_vector, constraints_vector, i, j)

pp_week <- pp_player %>% 
  group_by(gameweek, roster_id, Manager) %>% 
  summarise(pp = sum(potential_points)) %>% 
  left_join(matchup_id[, c('opponent_id', 'roster_id', 'gameweek')], by = c('gameweek', 'roster_id')) %>% 
  left_join(x=., y=.[, c('gameweek', 'opponent_id', 'pp')], by = c('gameweek', 'roster_id' = 'opponent_id')) %>% 
  rename(pp = pp.x, pp_opponent = pp.y) %>% 
  mutate(win = if_else(pp > pp_opponent, 1,
                       if_else(pp_opponent > pp, 0, 0.5)))

pp_season <- pp_week %>% 
  group_by(Manager) %>% 
  summarise(Wins = sum(win),
            Points = sum(pp)) %>% 
  arrange(desc(Wins), desc(Points)) %>% 
  mutate(Rank = seq.int(nrow(.))) %>% 
  select(Rank, Manager, Wins, Points)

pp_weekly_matchup <- pp_week %>% 
  filter(gameweek==gameweek_end) %>% 
  left_join(matchup_id[, c('matchup_id', 'roster_id', 'gameweek')], by = c('roster_id', 'gameweek')) %>% 
  left_join(x=., y=.[, c('Manager', 'opponent_id')], by = c('roster_id' = 'opponent_id')) %>% 
  mutate(roster_id  = as.numeric(roster_id)) %>% 
  arrange(matchup_id, roster_id) %>% 
  ungroup() %>% 
  filter(matchup_id==lead(matchup_id)) %>% 
  rename(pp.x = pp, pp.y = pp_opponent) %>% 
  select(-win, -roster_id, -opponent_id)

```

# Potential Points

The following table shows the potential points that could have been scored if the perfect squad had been played. The wins column shows how many wins each manager would have if every team played their perfect selection each week.

``` {r pp table, echo = F}

knitr::kable(pp_season, format = 'html', align = c('c', 'l', 'c', 'c')) %>% 
  kable_styling(bootstrap_options = c('striped', 'responsive'),
                full_width = F,
                position = 'left')

```

The matchups for week `r gameweek_end` are shown below, along with the potential points for each matchup.

```{r pp matchup, echo = F}

myHeader_init <- paste('Week ', gameweek_end, ' Potential Points Matchups', sep = '')
myHeader <- c(myHeader_init = 4)
names(myHeader) <- c(myHeader_init)

pp_weekly_matchup$Manager.x <- ifelse(pp_weekly_matchup$pp.x>pp_weekly_matchup$pp.y, cell_spec(pp_weekly_matchup$Manager.x, color = 'white', background = '#79c973', bold = T), cell_spec(pp_weekly_matchup$Manager.x, color = 'white', background = '#ff6666'))
pp_weekly_matchup$Manager.y <- ifelse(pp_weekly_matchup$pp.x<pp_weekly_matchup$pp.y, cell_spec(pp_weekly_matchup$Manager.y, color = 'white', background = '#79c973', bold = T), cell_spec(pp_weekly_matchup$Manager.y, color = 'white', background = '#ff6666'))

pp_weekly_matchup %>% 
  select(Manager.x, pp.x, pp.y, Manager.y) %>%
  knitr::kable(format = 'html', align = c('r', 'c', 'c', 'l'), col.names = NULL, escape = F) %>% 
  kable_styling(bootstrap_options = c('striped', 'responsive'),
                full_width = F,
                position = 'left') %>% 
  add_header_above(header = myHeader)
rm(myHeader, myHeader_init)

```
<br>

``` {r projected draft picks, echo = F}

picksRaw <- GET(paste("https://api.sleeper.app/v1/league/",league_id,"/traded_picks",sep=""))
picksParsed <- content(picksRaw, as="parsed")

datalist_picks = list()
for (i in 1:length(picksParsed)) {
  
  df <- data.frame(t(unlist(picksParsed[[i]])))
  
  datalist_picks[[i]] <- df
}
traded_picks <- bind_rows(datalist_picks)
rm(picksParsed, picksRaw, i, datalist_picks)

projected_draft <- pp_season %>% 
  left_join(pts_season[, c('Manager', 'Position')], by = 'Manager') %>% 
  rename(Actual_Position = Position) %>% 
  mutate(Temp_Rank = rank(if_else(Actual_Position<=6, as.double(Rank), as.double(Rank+100))),
         Rank = league_size + 1 - Temp_Rank) %>% 
  select(Rank, Manager) %>% 
  arrange(Rank) %>% 
  slice(rep(1:n(), each = 4)) %>% 
  mutate(Round = rep(c('1', '2', '3', '4'), league_size)) %>% 
  arrange(Round, Rank) %>% 
  left_join(user_info[, c('Manager', 'roster_id')], by = 'Manager') %>% 
  left_join(traded_picks[traded_picks$season==season+1,], by = c('roster_id', 'Round' = 'round')) %>% 
  left_join(user_info[, c('roster_id', 'Manager')], by = c('owner_id' = 'roster_id')) %>% 
  rename(Original_Owner = Manager.x, Owner = Manager.y, Pick = Rank) %>% 
  mutate(Owner = if_else(is.na(Owner), Original_Owner, Owner),
         `Original Owner` = if_else(Original_Owner==Owner, '', Original_Owner)) %>% 
  select(Round, Pick, Owner, `Original Owner`)

```
# Projected Draft Picks {.tabset .tabset-fade}

The `r draft_rounds` rounds of the `r (season+1)` rookie draft are shown below, using the potential points order as at today.

## Round 1

``` {r round1, echo=F}

projected_draft_table <- projected_draft %>%
  filter(Round==1)

projected_draft_table %>% 
  select(-Round) %>% 
  knitr::kable(format = 'html', align = c('c', 'l', 'c')) %>%
  kable_styling(bootstrap_options = c('striped', 'responsive'),
                full_width = F,
                position = 'left') %>% 
  row_spec(which(projected_draft_table$`Original Owner`!=''), bold = T, color = "white", background = "#feb9b9")

```

<br>

## Round 2
``` {r round2, echo=F}

projected_draft_table <- projected_draft %>%
  filter(Round==2)

projected_draft_table %>% 
  select(-Round) %>% 
  knitr::kable(format = 'html', align = c('c', 'l', 'c')) %>%
  kable_styling(bootstrap_options = c('striped', 'responsive'),
                full_width = F,
                position = 'left') %>% 
  row_spec(which(projected_draft_table$`Original Owner`!=''), bold = T, color = "white", background = "#feb9b9")

```

<br>

## Round 3
``` {r round3, echo=F}

projected_draft_table <- projected_draft %>%
  filter(Round==3)

projected_draft_table %>% 
  select(-Round) %>% 
  knitr::kable(format = 'html', align = c('c', 'l', 'c')) %>%
  kable_styling(bootstrap_options = c('striped', 'responsive'),
                full_width = F,
                position = 'left') %>% 
  row_spec(which(projected_draft_table$`Original Owner`!=''), bold = T, color = "white", background = "#feb9b9")

```

<br>

## Round 4
``` {r round4, echo=F}

projected_draft_table <- projected_draft %>%
  filter(Round==4)

projected_draft_table %>% 
  select(-Round) %>% 
  knitr::kable(format = 'html', align = c('c', 'l', 'c')) %>%
  kable_styling(bootstrap_options = c('striped', 'responsive'),
                full_width = F,
                position = 'left') %>% 
  row_spec(which(projected_draft_table$`Original Owner`!=''), bold = T, color = "white", background = "#feb9b9")
rm(projected_draft_table)
## {-}
```

<br>

# 2021 Trade Count

```{r trades, echo=F}

transactions <- ff_transactions(dynasty_conn) %>% 
  left_join(user_info[, c('roster_id', 'Manager')], by = c('franchise_id' = 'roster_id'))

transactions %>% 
  filter(type == 'trade') %>% 
  select(timestamp, type, Manager) %>% 
  distinct() %>%
  group_by(Manager) %>% 
  summarise(Trade_Count = n()) %>%
  arrange(desc(Trade_Count)) %>% 
  plot_ly(y = ~Trade_Count) %>% 
  add_trace(x = ~Manager, type = 'bar') %>% 
  layout(title = ' Number of 2021 Trades by Team',
         xaxis = list(title = 'Team', categoryorder = "array", categoryarray = ~Trade_Count, fixedrange = TRUE),
         yaxis = list(title = 'Number of Trades', fixedrange = TRUE))

```